CDS-abstract-figure

### 2021-11-13 conference/CDS-abstract-figure.Rmd
all figures added for CDS

figA<-read_rds('../group-d/output/ETfig.rds')
figB<-read_rds('../group-b/output/ETfig.rds')
figC<-read_rds('../group-d/output/ETfig.rds')
figD<-read_rds('../group-d/output/ETfig.rds')
figE<-read_rds('../group-d/output/ETfig.rds')

```{r}
A <- displayA + figA 
B <- displayB + figB 
C <- displayC + figC 
D <- displayD + figD 
E <- displayE + figE

@@

```{r}
ggsave('CDS-abstract-figure.pdf', scale = 1, width = 12, height = 7)

>>>>

figA<-read_rds('../group-a/output/exp1_plot.rds')
figB<-read_rds('../group-b/output/ETfig.rds')
figC<-read_rds('../group-c/output/exp3_plot.rds')+scale_color_brewer(palette = "Set1")
figD<-read_rds('../group-d/output/ETfig.rds')
figE<-read_rds('../group-e/output/exp5_plot.rds')+scale_color_brewer(palette = "Set1")

figA.1<-ggplot(figA$data, 
               aes(x=t.window, y=cumulative.fixation.m, shape = object_class, color = verb_type))+
  geom_point(size=1)+
  geom_line()+
  scale_color_brewer(palette = "Set1", name = "Verb type")+
  scale_shape_manual(name = "Gaze location", values = c(1,4), labels = c("distractor", "target"))+
  theme_classic()+
  labs(x = "Time from Verb Onset", y="Cumulative Look Probability")
figA.1
```

```{r}
A <- displayA + figA.1 + plot_layout(widths = c(1.5,1)) & theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
B <- displayB + figB + plot_layout(widths = c(1.5,1)) & theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
C <- displayC + figC + plot_layout(widths = c(1.5,1)) & theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
D <- displayD + figD + plot_layout(widths = c(1.5,1)) & theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
E <- displayE + figE + plot_layout(widths = c(1.5,1)) & theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))

@@

```{r}
ggsave('CDS-abstract-figure.pdf', width = 11.5, height = 7)
